---
title: "Exercise 2.2"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Exercise 2.2 Ploting in ggplot
```{r}
library(ggplot2)
library(tidyverse)
```

# 1. Add best fit lines to our msleep plot for each order.
```{r}
ggplot(msleep, aes(y=sleep_total, x=sleep_rem, group=as.factor(vore), color=as.factor(vore)))+
  geom_point()+
  labs(y="Total Sleep (hours)", x="REM Sleep (hours")+
  theme_classic()+
  #scale_color_manual(values=rainbow(5))
  scale_color_manual(name="Diet", 
                     labels = c("Carnivore", 
                                "Herbivore", 
                                "Insectivore", 
                                "Omnivore", 
                                "NA"), 
                     values = c("carni"="blue", 
                                "herbi"="red", 
                                "insecti"="green", 
                                "omni"="brown", 
                                "NA"="orange"))+
  geom
```

  
# 2. In the msleep data, make a boxplot of sleep_total against vore. Make sure vore is a factor. Color the boxplots by vore (remember how we had to color the boxplots in base R) it is similar in ggplot.  



# 3. Load a new dataframe `midwest`(run data(midwest)) and plot a scatterplot of area against popdensity grouped and color by state. Do a facet grid by state.



#  4. In the midwest dataframe make a scatterplot of the popdensity by poptotal of only IL (this requires you to subset your data for illinois).




# 5. In the midwest dataframe plot the mean and standard error for popdensity for each state. Color this plot in your favorite palette.